The ensmallen library for flexible numerical optimization

### 2021-07-06 final_submission/20-416.tex
Freeze the Minted cache so JMLR's service can compile things.
Merge #7 into the final submission.

\usepackage{jmlr2e}
\usepackage{minted}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{booktabs}      % for \toprule in tables
\usepackage{multirow}      % for table multirow
\usepackage{tcolorbox}   % colorbox in minted
\usepackage{parcolumns}
\usepackage{adjustbox}
\usepackage{nicefrac}
\usepackage{tabularx}
\usepackage{array}
\usepackage{wasysym}
\usepackage{dcolumn}

@@

The problem of numerical optimization is generally expressed as
$\operatornamewithlimits{argmin}_x f(x)$
where $f(x)$ is a given objective function and $x$ is typically a vector or matrix.
Such optimization problems are fundamental and ubiquitous in the computational sciences~\citep{Nocedal_2006}.
Many frameworks or libraries for specific machine learning approaches
have an integrated optimization component for distinct and limited use cases,
such as
TensorFlow~\citep{TensorFlow_arXiv_2016},
PyTorch~\citep{PyTorch_NeurIPS_2019}
and LibSVM~\citep{libsvm2011}.
There are also many general numerical optimization toolkits
aimed at supporting a wider range of use cases,
including SciPy~\citep{SciPy_NMeth_2020},
opt++~\citep{meza1994opt++},
and 
OR-Tools~\citep{ortools} among many others.
% CVXOPT~\citep{vandenberghe2010cvxopt},
%NLopt~\citep{johnson2014nlopt}, Ceres~\citep{ceres-solver},
%% {\tt fminsearch()} in MATLAB~\cite{matlab_fminsearch},
%and RBFOpt~\citep{costa2018rbfopt}.
However, such toolkits still have limitations in several areas,
including:
(i)~types of supported objective functions,
(ii)~selection of available optimizers,
(iii)~support for custom behavior via callback functions,
(iv)~support for various underlying element and matrix types used by objective functions.
and
(v)~extensibility, to facilitate adding more optimizers.

@@

Further details, such as internal use of template metaprogramming
for automatic generation of efficient code, automatic function inference,
clean error reporting, and various approaches for obtaining efficiency
are discussed in the accompanying technical report~\citep{ensmallen2020}.

>>>>

\usepackage{jmlr2e}
\usepackage[frozencache]{minted}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{booktabs}      % for \toprule in tables
\usepackage{multirow}      % for table multirow
\usepackage{tcolorbox}   % colorbox in minted
\usepackage{parcolumns}
\usepackage{adjustbox}
\usepackage{nicefrac}
\usepackage{tabularx}
\usepackage{array}
\usepackage{wasysym}
\usepackage{dcolumn}

@@

The problem of numerical optimization is generally expressed as
$\operatornamewithlimits{argmin}_x f(x)$
where $f(x)$ is a given objective function and $x$ is typically a vector or matrix.
Such optimization problems are fundamental and ubiquitous in the computational sciences~\citep{Nocedal_2006}.
Many frameworks or libraries for specific machine learning approaches
have an integrated optimization component for distinct and limited use cases,
such as
TensorFlow~\citep{TensorFlow_arXiv_2016},
PyTorch~\citep{PyTorch_NeurIPS_2019}
and LibSVM~\citep{libsvm2011}.
There are also many general numerical optimization toolkits
aimed at supporting a wider range of use cases,
including SciPy~\citep{SciPy_NMeth_2020},
opt++~\citep{meza1994opt++},
and 
OR-Tools~\citep{ortools} among many others.
% CVXOPT~\citep{vandenberghe2010cvxopt},
%NLopt~\citep{johnson2014nlopt}, Ceres~\citep{ceres-solver},
%% {\tt fminsearch()} in MATLAB~\cite{matlab_fminsearch},
%and RBFOpt~\citep{costa2018rbfopt}.
However, such toolkits still have limitations in several areas,
including:
(i)~types of supported objective functions,
(ii)~selection of available optimizers,
(iii)~support for custom behavior via callback functions,
(iv)~support for various underlying element and matrix types used by objective functions,
and
(v)~extensibility, to facilitate adding more optimizers.

@@

Further details, such as internal use of template metaprogramming
for automatic generation of efficient code, automatic function inference,
clean error reporting, and various approaches for obtaining efficiency
are all discussed in the accompanying technical report~\citep{ensmallen2020}.
